---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Get Census Tract ID for Exact Locations

<!-- badges: start -->
[![R-CMD-check](https://github.com/geomarker-io/tract/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/geomarker-io/tract/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/tract)](https://CRAN.R-project.org/package=tract)
<!-- badges: end -->

## Installation

You can install the development version of tract from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("geomarker-io/tract")
```

## Example

In R, get census tract identifiers for exact locations and years using the `get_census_tract_id()` function:

```{r example}
library(tract)

get_census_tract_id(
  s2::as_s2_cell(c("8841b399ced97c47", "8841b38578834123")), 
  year = "2020")
```

## S2 geohash

The [s2 geohash](https://s2geometry.io/) is a [hierarchical](https://s2geometry.io/devguide/s2cell_hierarchy.html) geospatial index that uses [spherical geometry](https://s2geometry.io/about/overview). In R, s2 cells can be [created](https://r-spatial.github.io/s2/reference/s2_cell.html#ref-examples) using their character string representation, or by specifying latitude and longitude coordinates; e.g.:

```{r}
s2::s2_lnglat(c(-84.4126, -84.5036), c(39.1582, 39.2875)) |> s2::as_s2_cell()
```
